---
title: "priorityPlaces"
author: "Tati Micheltti and Alex Chubaty"
date: "28 February 2020"
output: pdf_document
editor_options: 
  chunk_output_type: console
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## Solver information

See <https://prioritizr.net/articles/prioritizr.html#add-a-solver> for a discussion on the different solvers available for this module.

### Gurobi

See <https://prioritizr.net/articles/gurobi_installation.html> for installation instructions.
Requires free academic or paid commercial license, and installation of both the Gurobi software and corresponding R package.

*NOTE:* the `gurobi` package will fail to load in an Rstudio desktop session.

### `Rsymphony`

Requires COIN-OR Symphony header and development libraries.
For Ubuntu 18.04 these can be installed via:

```bash
sudo apt install coinor-libsymphony-dev
```

Afterwards, a user must install the `Rsymphony` package from CRAN with `install.packages("Rsymphony")`.

### `lpsymphony`

Requires installation of the `lpsymphony` package from Bioconductor (<https://doi.org/doi:10.18129/B9.bioc.lpsymphony>).

```r
if (!requireNamespace("BiocManager", quietly = TRUE))
  install.packages("BiocManager")

BiocManager::install("lpsymphony")
```

# Usage

```{r module_usage}
library(SpaDES.core)
library(SpaDES.tools)

library("raster")
library("reproducible")
library("SpaDES.core")
library("SpaDES.tools")
library("usefun")
library("googledrive")
library("data.table")

drive_auth("tati.micheletti@gmail.com")
# scratchDir <- file.path("/mnt/tmp")

options(reproducible.cacheSaveFormat = "rds")

setPaths(modulePath = file.path(getwd(), "modules"),
         inputPath = file.path(getwd(), "inputs"),
         cachePath = file.path(getwd(), "cache"),
         outputPath = file.path(getwd(), "outputs"))
getPaths() # shows where the 4 relevant paths are
options(reproducible.showSimilar = FALSE)

times <- list(start = 2011, end = 2100)

parameters <- list(
  priorityPlaces = list(".useCache" = FALSE,
                        "stepInterval" = 89,
                        "binaryDecision" = FALSE,
                        "constraintType" = list(
                          #add_locked_in_constraints = list(locked_in = c(50, 53, 52, 51)),
                          #add_feature_contiguity_constraints = NULL,
                          #add_neighbor_constraints = list(k = 2),
                          #add_locked_out_constraints = list(locked_out = c(3, 4, 13, 14))
                        ),
                        "fasterOptimization" = TRUE,
                        "firstFeasible" = FALSE,
                        "penalty" = NULL, ## used to penalize highly fragmented solutions
                        "presolve" = 2,
                        "solutions" = 1, ## converges on a single solution already
                        #"solver" = "rsymphony", ## change accordingly
                        "targets" = c(0.15, 0.2), ## streams 1, 2
                        "timeLimit" = 1800,
                        "verbose" = TRUE,
                        ".plotInitialTime" = NA
  )
)

fold <- "C:/Users/Tati/Google Drive/Postdoc PFC-UBC/NWT 2019/G&C_Contract/priorityPlacesPreliminaryResults/rawNoWeight/"
featuresID_2011 <- stack(file.path(fold, "featuresID_2011_noWeight.grd"))
featuresID_2100 <- stack(file.path(fold, "featuresID_2100_noWeight.grd"))
planningUnit_2011 <- raster(file.path(fold, "planningUnit_2011_noWeight.tif"))
planningUnit_2100 <- raster(file.path(fold, "planningUnit_2100_noWeight.tif"))

modules <- list("priorityPlaces")
objects <- list(
  
)
inputs <- list()
outputs <- list()

mySim <- simInitAndSpades(times = times, params = parameters, modules = modules, objects = objects)
```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams}
df_params <- moduleParams("priorityPlaces", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("priorityPlaces", "path/to/modules/dir")` may be sufficient.

```{r moduleInputs}
df_inputs <- moduleInputs("priorityPlaces", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs}
df_outputs <- moduleOutputs("priorityPlaces", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
