---
title: "priorityPlaces"
author: ""
date: "28 February 2020"
output: pdf_document
---

# Overview

Provide an overview of what the module does / how to use the module.

Module documentation should be written so that others can use your module.
This is a template for module documentation, and should be changed to reflect your module.

## R Markdown

R Markdown syntax allows R code, outputs, and figures to be rendered in the documentation.

For help writing in R Markdown, see http://rmarkdown.rstudio.com/.

# Usage

```{r module_usage}
library(SpaDES)

setPaths(modulePath = file.path(dirname(getwd())))
getPaths() # shows where the 4 relevant paths are

times <- list(start = 0, end = 0)

parameters <- list(
  priorityPlaces = list(".useCache" = TRUE,
                        "fasterOptimization" = FALSE,
                        "targets" = c(0.35, 0.1, 0.2),
                        "binaryDecision" = FALSE,
                        "constraintType" = list(add_locked_in_constraints = list(locked_in = c(50, 53, 
                                                                                               52, 51)),
                                                # add_feature_contiguity_constraints = NULL,
                                                # add_neighbor_constraints = list(k = 2),
                                                add_locked_out_constraints = list(locked_out = c(3, 4, 
                                                                                               13, 14))),
                        "penalty" = 0.1,
                        "firstFeasible" = FALSE)
)

modules <- list("priorityPlaces")
objects <- list()
inputs <- list()
outputs <- list()

mySim <- simInitAndSpades(times = times, params = parameters, modules = modules,
                 objects = objects)

```

# Parameters

Provide a summary of user-visible parameters.

```{r moduleParams}
df_params <- moduleParams("priorityPlaces", "..")
knitr::kable(df_params)
```

# Events

Describe what happens for each event type.

## Plotting

Write what is plotted.

## Saving

Write what is saved.

# Data dependencies

## Input data

How to obtain input data, and a description of the data required by the module.
If `sourceURL` is specified, `downloadData("priorityPlaces", "path/to/modules/dir")` may be sufficient.

```{r moduleInputs}
df_inputs <- moduleInputs("priorityPlaces", "..")
knitr::kable(df_inputs)
```

## Output data

Description of the module outputs.

```{r moduleOutputs}
df_outputs <- moduleOutputs("priorityPlaces", "..")
knitr::kable(df_outputs)
```

# Links to other modules

Describe any anticipated linkages to other modules.
